Supervised Learning for Psychological Attention to High School Students

### 2020-11-18 article/article.tex
[ article ] added performance tables.

Additionally, it is well-known that the bound for the training dataset size is
given by
\begin{equation}
  N\geq \dfrac{\ln(2)}{2\epsilon^2}\left[(2^k-1)(1+\log_2 m) + 1 + \ln\left(
  \dfrac{1}{\delta}\right)\right],
\end{equation}
but again, the size of the dataset is fixed,

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

Additionally, it is well-known that the bound for the training dataset size is
given by
\begin{equation}
  N\geq \dfrac{\ln(2)}{2\epsilon^2}\left[(2^k-1)(1+\log_2 m) + 1 + \ln\left(
  \dfrac{1}{\delta}\right)\right],
\end{equation}
but again, the size of the dataset is fixed. Thus, $\epsilon$ was calculated by
fixing the tree depth $k$ and setting $\delta=0.7$.............

@@

\begin{table}
\centering
\caption{Performance scores for linear SVM.}
\label{tab:linear_SVM}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & 0 & 1 \\
Testing & 0 & 1 \\
Validation & 0 & 1 \\ \hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Performance scores for polynomial SVM.}
\label{tab:poly_SVM}
\begin{tabular}{cll}
\hline
\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
Training & 0.89 & 1 \\
Testing & 0 & 1 \\
Validation & 0.57 & 1 \\ \hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Performance scores for RBF SVM.}
\label{tab:rbf_SVM}
\begin{tabular}{cll}
\hline
\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
Training & 0.13 & 1 \\
Testing & 0 & 1 \\
Validation & 0.25 & 1 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}
\centering
\caption{Performance scores for DT.}
\label{tab:DT}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
Training & 1 & 1 \\
Testing & 0.5 & 1 \\
Validation & 0.75 & 1 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}
\centering
\caption{Performance scores for $\mathcal{L}=[3]$ and $\eta=0.9$.}
\label{tab:L3}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & 0.5 & 1 \\
Testing & $\times$ & 1 \\
Validation & 1 & 1 \\ \hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Performance scores for $\mathcal{L}=[2]$ and $\eta=0.9$.}
\label{tab:L2}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & $\times$ & 1 \\
Testing & $\times$ & 1 \\
Validation & $\times$ & 1 \\ \hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Performance scores for $\mathcal{L}=[1,2,3]$ and $\eta=0.9$.}
\label{tab:L123}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & 0 & 1 \\
Testing & 0 & 1 \\
Validation & 0 & 1 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}
\centering
\caption{Performance scores for linear SVM.}
\label{tab:linear_SVM_emb}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & 0 & 1 \\
Testing & 0 & 1 \\
Validation & 0 & 1 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}
\centering
\caption{Performance scores for polynomial SVM.}
\label{tab:poly_SVM_emb}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & 0 & 1 \\
Testing & 0 & 1 \\
Validation & 0 & 1 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}
\centering
\caption{Performance scores for polynomial RBF.}
\label{tab:rbf_SVM_emb}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & 0 & 1 \\
Testing & 0 & 1 \\
Validation & 0 & 1 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}
\centering
\caption{Performance scores for DT.}
\label{tab:DT_emb}
\begin{tabular}{cll}
\hline
\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
Training & 1 & 1 \\
Testing & 0 & 1 \\
Validation & 0.63 & 0.94 \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}
\centering
\caption{Performance scores for $\mathcal{L}=[2]$ and $\eta=0.2$.}
\label{tab:L2_emb}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & $\times$ & 1 \\
Testing & $\times$ & 1 \\
Validation & $\times$ & 1 \\ \hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Performance scores for $\mathcal{L}=[3]$ and $\eta=0.5$.}
\label{tab:L3_emb}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & $\times$ & 1 \\
Testing & $\times$ & 1 \\
Validation & $\times$ & 1 \\ \hline
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{Performance scores for $\mathcal{L}=[2,3,3]$ and $\eta=0.9$.}
\label{tab:L233_emb}
\begin{tabular}{ccc}
\hline
\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
Training & 0 & 1 \\
Testing & 0 & 1 \\
Validation & 0 & 1 \\ \hline
\end{tabular}
\end{table}
